rejected_text

### 2024-09-30 paper/rejected-text.qmd
draft of Abstract through Methods

@@

>>>>

## rejected from intro

(e.g., Paris mayor Anne Hidalgo proposed plan in her 2020 re-election campaign [@teixeiraClassifying15minuteCities2024], neighbourhood guidance in Shanghai, China [@weng15minuteWalkableNeighborhoods2019])

@@

Furthermore, mobility of care trip characteristics differ from other trips, notably those of the commute to work. For instance, many of these trips are made through trip-chains, i.e., when a non-work-related stop is made during the commute. Women have been found to do so more than men, which is understood as being due to their need to balance unpaid-household serving care and paid employment (e.g., picking up groceries or children on the way home from work) [@ravensbergen2023exploratory; @scheinerWomenComplexDaily2015].
